Something

### 2019-05-10 cysep-eurosp/abstract.tex
some more text

\textbf{Problem:}
Crowd counts vary according to who is doing the counting and what
methods and criteria they use. Current methods have wide margins for
error, are difficult to verify, and can be privacy-invasive. We
recognize the potential adversarial setting for crowd counts and thus
aim for both transparency (in the form of verifiability) and
privacy. Different counts: Any solution

@@

\textbf{Preliminary results:} We find that, with some
 assumptions about the availability of future technology such as
 distance-bounding chips on smartphones, CROCUS can provide the
 desired properties at acceptable performance.

\textbf{Relation to theme:} This work is concerned with both security
and privacy: accountability and verifiability (individual, universal, eligibility) and
privacy (unlinkability to individual, unlinkability between events,
unlinkability between witnessing instances).

\textbf{Why it could spark discussions:}
practical/ideological problems: sybil-proof identities needed for anonymous
credentials

>>>>

\textbf{Problem:}
Crowd counts vary according to who is doing the counting and what
methods and criteria they use. Current methods have wide margins for
error, are difficult to verify, and can be
privacy-invasive. Historically, there are many examples of events such
as protests in which the count estimated by police and that of the
organizers differ significantly, sometimes by hundreds of
thousands. Even without foul play, the difference is quite natural as
both parties have different objectives and metrics. More precisely,
the organizers want to count everyone who participated while the
police want to estimate the count at the peak of participation, due to
crowd control. We
recognize the potential adversarial setting for crowd counts and thus
aim for both transparency (in the form of verifiability) and
privacy. Since the crowd count could be done at political protests,
any solution needs to not endanger participants more than what they
already face by their physical presence.

@@

\textbf{Preliminary results:} We find that, with some
 assumptions about the availability of future technology such as
 distance-bounding chips on smartphones, CROCUS can provide the
 desired properties at acceptable performance, except against a truly
 global passive adversary.

\textbf{Relation to theme:} This work is concerned with both security
and privacy: accountability and verifiability (individual, universal, eligibility) and
privacy (unlinkability to individual, unlinkability between events,
unlinkability between witnessing instances). The building blocks are
anonymous credentials, distance bounding, blockchain (or other public ledger)

\textbf{Why it could spark discussions:} There are some practical
problems that might also be ideological problems: to ensure
verifiability (specifically, eligibitlity of counting only once, in
analogy to votes or double spending in e-currencies) despite
unlinkability/privacy properties, we need sybil-proof identities for
anonymous credentials.
